Fourmile Calibrations and Output

### 2024-12-27 fourmile_output_dec2024.Rmd
cals for dec2024 updates

## Density plots

@@

```{r hydrographs, echo = FALSE, message = FALSE, warning = FALSE}

setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates')

@@

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            "grid_2011"="seagreen",
                                            "grid_2012"="seagreen2",
                                            "grid_2013"="steelblue",
                                            "grid_2014"='dodgerblue',
                                            "grid_2015" = "cyan3",
                                            'grid_2016' = 'blue',
                                            'grid_2017' = 'blue4',
                                            'grid_2018' = 'cadetblue',
                                            'grid_2019' = 'lightgreen',
                                            'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            "statn_2011"="maroon",
                                            "statn_2012"="deeppink4",
                                            "statn_2013"="deeppink",
                                            "statn_2014"='purple',
                                            "statn_2015" = "mediumorchid1",
                                            'statn_2016' = 'indianred',
                                            'statn_2017' = 'sienna',
                                            'statn_2018' = 'salmon2',
                                            'statn_2019' = 'mediumpurple1',
                                            'statn_2020' = 'violetred',
                                            'statn_all' = 'red'))

@@

#plot annual cumulative Q vals for ensembles
plot_cumulq_yr_ <- function(calyear) {
  {flow_cumq %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = cumsum,
               color = cal_run)) +
    geom_line() +
scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            "grid_2011"="seagreen",
                                            "grid_2012"="seagreen2",
                                            "grid_2013"="steelblue",
                                            "grid_2014"='dodgerblue',
                                            "grid_2015" = "cyan3",
                                            'grid_2016' = 'blue',
                                            'grid_2017' = 'blue4',
                                            'grid_2018' = 'cadetblue',
                                            'grid_2019' = 'lightgreen',
                                            'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            "statn_2011"="maroon",
                                            "statn_2012"="deeppink4",
                                            "statn_2013"="deeppink",
                                            "statn_2014"='purple',
                                            "statn_2015" = "mediumorchid1",
                                            'statn_2016' = 'indianred',
                                            'statn_2017' = 'sienna',
                                            'statn_2018' = 'salmon2',
                                            'statn_2019' = 'mediumpurple1',
                                            'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
    ggtitle(calyear) +
    theme_bw() +
    labs(y = 'Volume (m^3)')} %>%
    ggplotly()
}

@@

flow_kge_all <- flow %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

### Annual KGE plots

```{r wy plots, echo = FALSE, message = FALSE, warning = FALSE}

plot_kge <- function(calyear) {
  flow_plot %>%
    filter(year == calyear) %>%
    ggplot(aes(x = model_run,
               y = kge)) +
    geom_point(size=3) +
    ggtitle(calyear) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1))
}

name <- levels(flow_plot$year)

lapply(name, plot_kge)

@@

flow_pbias_all <- flow %>%
  summarize(grid2011 = pbias(grid_2011, obs),
            grid2012 = pbias(grid_2012, obs),
            grid2013 = pbias(grid_2013, obs),
            grid2014 = pbias(grid_2014, obs),
            grid2015 = pbias(grid_2015, obs),
            grid2016 = pbias(grid_2016, obs),
            grid2017 = pbias(grid_2017, obs),
            grid2018 = pbias(grid_2018, obs),
            grid2019 = pbias(grid_2019, obs),
            grid2020 = pbias(grid_2020, obs),
            gridall = pbias(grid_all, obs),
            statn2011 = pbias(statn_2011, obs),
            statn2012 = pbias(statn_2012, obs),
            statn2013 = pbias(statn_2013, obs),
            statn2014 = pbias(statn_2014, obs),
            statn2015 = pbias(statn_2015, obs),
            statn2016 = pbias(statn_2016, obs),
            statn2017 = pbias(statn_2017, obs),
            statn2018 = pbias(statn_2018, obs),
            statn2019 = pbias(statn_2019, obs),
            statn2020 = pbias(statn_2020, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(grid2011 = pbias(grid_2011, obs),
            grid2012 = pbias(grid_2012, obs),
            grid2013 = pbias(grid_2013, obs),
            grid2014 = pbias(grid_2014, obs),
            grid2015 = pbias(grid_2015, obs),
            grid2016 = pbias(grid_2016, obs),
            grid2017 = pbias(grid_2017, obs),
            grid2018 = pbias(grid_2018, obs),
            grid2019 = pbias(grid_2019, obs),
            grid2020 = pbias(grid_2020, obs),
            gridall = pbias(grid_all, obs),
            statn2011 = pbias(statn_2011, obs),
            statn2012 = pbias(statn_2012, obs),
            statn2013 = pbias(statn_2013, obs),
            statn2014 = pbias(statn_2014, obs),
            statn2015 = pbias(statn_2015, obs),
            statn2016 = pbias(statn_2016, obs),
            statn2017 = pbias(statn_2017, obs),
            statn2018 = pbias(statn_2018, obs),
            statn2019 = pbias(statn_2019, obs),
            statn2020 = pbias(statn_2020, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

### Annual Pbias plots

```{r pbias plots, echo = FALSE, message = FALSE, warning = FALSE}

plot_pbias <- function(calyear) {
  flow_plot %>%
    filter(year == calyear) %>%
    ggplot(aes(x = model_run,
               y = pbias)) +
    geom_point(size=3) +
    ggtitle(calyear) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1))
}

name <- levels(flow_plot$year)

lapply(name, plot_pbias)

<!-- # Ensembles -->

<!-- ## Hydrograph -->

<!-- ```{r ensemble hydrographs, echo = F} -->

<!-- ensem <- flow %>% -->
<!--   rowwise() %>% -->
<!--   mutate(grid_ensemble = mean(c(grid_2011, grid_2012, -->
<!--                                 grid_2013, grid_2014, -->
<!--                                 grid_2015, grid_2016, -->
<!--                                 grid_2017, grid_2018, -->
<!--                                 grid_2019, grid_2020)), -->
<!--          statn_ensemble = mean(c(statn_2011, statn_2012, -->
<!--                                  statn_2013, statn_2014, -->
<!--                                  statn_2015, statn_2016, -->
<!--                                  statn_2017, statn_2018, -->
<!--                                  statn_2019, statn_2020)), -->
<!--          all_ensemble = mean(c(grid_2011, grid_2012, -->
<!--                                grid_2013, grid_2014, -->
<!--                                grid_2015, grid_2016, -->
<!--                                grid_2017, grid_2018, -->
<!--                                grid_2019, grid_2020, -->
<!--                                statn_2011, statn_2012, -->
<!--                                statn_2013, statn_2014, -->
<!--                                statn_2015, statn_2016, -->
<!--                                statn_2017, statn_2018, -->
<!--                                statn_2019, statn_2020, -->
<!--                                grid_all, statn_all))) %>% -->
<!--   dplyr::select(date, grid_ensemble, statn_ensemble, -->
<!--          all_ensemble, grid_all, -->
<!--          statn_all, obs) -->

<!-- ensem_pivot <- ensem %>% -->
<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
<!--   mutate(year = as.factor(year(date))) -->

<!-- q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) + -->
<!--   geom_line() + -->
<!--   scale_color_manual(name="cal_run", values=c('obs'='black', -->
<!--                                             "grid_ensemble"="maroon", -->
<!--                                             "statn_ensemble"="darkturquoise", -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4', -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--   scale_y_continuous(name = 'Q_m3s') + -->
<!--   theme_bw() -->

<!-- q_ensemble -->

<!-- ## KGE -->

<!-- ### KGE for ensembles (entire period) -->

<!-- ```{r ensemble kge, echo = F} -->

<!-- ensem_kge_all <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
<!--             all_ensemble = KGE(all_ensemble, obs), -->
<!--             grid_all = KGE(grid_all, obs), -->
<!--             statn_all = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- kable(ensem_kge_all) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- ### Annual KGEs for ensembles -->

<!-- ```{r annual kge ensemble, echo = F} -->

<!-- yr_kge_ensem <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   group_by(year) %>% -->
<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
<!--             all_ensemble = KGE(all_ensemble, obs), -->
<!--             grid_all = KGE(grid_all, obs), -->
<!--             statn_all = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- yr_kge_table <- yr_kge_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
<!--   pivot_wider(names_from = 'year', values_from = 'kge') -->

<!-- yr_kge_table %>% -->
<!--   kable(.) %>% -->
<!--   kable_styling() -->

<!-- yr_kge_plot <- yr_kge_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
<!--   mutate(year = as.factor(year)) -->

<!-- #plot annual kge vals for ensembles -->
<!-- plot_kge_yr_ensem <- function(calyear) { -->
<!--   yr_kge_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = kge)) + -->
<!--     geom_col() + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(yr_kge_plot$year) -->

<!-- lapply(name, plot_kge_yr_ensem) -->

<!-- ### Monthly KGEs for ensembles -->

<!-- ```{r monthly kge ensemble, echo = F} -->

<!-- mo_kge <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   drop_na() %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   group_by(month) %>% -->
<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
<!--             all_ensemble = KGE(all_ensemble, obs), -->
<!--             grid_all = KGE(grid_all, obs), -->
<!--             statn_all = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- kable(mo_kge) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- mo_pivot <- mo_kge %>% -->
<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'KGE') %>% -->
<!--   drop_na() -->

<!-- kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) + -->
<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
<!--                                             "statn_ensemble"="darkturquoise", -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4', -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--   theme_bw() -->

<!-- ggplotly(kge_plot_mo) -->

<!-- ## RMSE -->

<!-- ### Ensemble RMSE for entire period -->

<!-- ```{r ensemble rmse, echo = F} -->

<!-- ensem_rmse_all <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
<!--             all_ensemble = rmse(all_ensemble, obs), -->
<!--             grid_all = rmse(grid_all, obs), -->
<!--             statn_all = rmse(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 4) -->

<!-- kable(ensem_rmse_all) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- ### Annual RMSE for ensembles -->

<!-- ```{r annual rmse ensem, echo = F} -->

<!-- yr_rmse_ensem <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   group_by(year) %>% -->
<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
<!--             all_ensemble = rmse(all_ensemble, obs), -->
<!--             grid_all = rmse(grid_all, obs), -->
<!--             statn_all = rmse(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 4) -->

<!-- yr_rmse_table <- yr_rmse_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
<!--   pivot_wider(names_from = 'year', values_from = 'rmse') -->

<!-- yr_rmse_table %>% -->
<!--   kable(.) %>% -->
<!--   kable_styling() -->

<!-- yr_rmse_plot <- yr_rmse_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
<!--   mutate(year = as.factor(year)) -->

<!-- #plot annual rmse vals for ensembles -->
<!-- plot_rmse_yr_ensem <- function(calyear) { -->
<!--   yr_rmse_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = rmse)) + -->
<!--     geom_col() + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(yr_rmse_plot$year) -->

<!-- lapply(name, plot_rmse_yr_ensem) -->

<!-- ### Monthly RMSEs for ensembles -->

<!-- ```{r month ensem rmse, echo = F} -->

<!-- mo_rmse <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   drop_na() %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   group_by(month) %>% -->
<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
<!--             all_ensemble = rmse(all_ensemble, obs), -->
<!--             grid_all = rmse(grid_all, obs), -->
<!--             statn_all = rmse(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 4) -->

<!-- kable(mo_rmse) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- mo_pivot2 <- mo_rmse %>% -->
<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'RMSE') %>% -->
<!--   drop_na() -->

<!-- rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) + -->
<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
<!--                                             "statn_ensemble"="darkturquoise", -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4', -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--   theme_bw() -->

<!-- ggplotly(rmse_plot_mo) -->

<!-- ## NSE -->

<!-- ### Ensemble NSE for entire period -->

<!-- ```{r nse all, echo = F} -->

<!-- ensem_nse_all <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
<!--             all_ensemble = NSE(all_ensemble, obs), -->
<!--             grid_all = NSE(grid_all, obs), -->
<!--             statn_all = NSE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- kable(ensem_nse_all) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- ### Annual NSE for ensembles -->

<!-- ```{r annual nse, echo = F} -->

<!-- yr_nse_ensem <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   group_by(year) %>% -->
<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
<!--             all_ensemble = NSE(all_ensemble, obs), -->
<!--             grid_all = NSE(grid_all, obs), -->
<!--             statn_all = NSE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 4) -->

<!-- yr_nse_table <- yr_nse_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
<!--   pivot_wider(names_from = 'year', values_from = 'nse') -->

<!-- yr_nse_table %>% -->
<!--   kable(.) %>% -->
<!--   kable_styling() -->

<!-- yr_nse_plot <- yr_nse_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
<!--   mutate(year = as.factor(year)) -->

<!-- #plot annual nse vals for ensembles -->
<!-- plot_nse_yr_ensem <- function(calyear) { -->
<!--   yr_nse_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = nse)) + -->
<!--     geom_col() + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(yr_nse_plot$year) -->

<!-- lapply(name, plot_nse_yr_ensem) -->

<!-- ### Monthly NSE for ensembles -->

<!-- ```{r monthly rmse, echo =F} -->

<!-- mo_nse <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   drop_na() %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   group_by(month) %>% -->
<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
<!--             all_ensemble = NSE(all_ensemble, obs), -->
<!--             grid_all = NSE(grid_all, obs), -->
<!--             statn_all = NSE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 4) -->

<!-- kable(mo_nse) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- mo_pivot2 <- mo_nse %>% -->
<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'nse') %>% -->
<!--   drop_na() -->

<!-- nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) + -->
<!--   theme_bw() + -->
<!--   scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
<!--                                             "statn_ensemble"="darkturquoise", -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4', -->
<!--                                             "all_ensemble" = "orange")) -->

<!-- ggplotly(nse_plot_mo) -->

<!-- # Catchment results -->

<!-- ## Precip -->

<!-- ```{r catch precip, echo = F} -->
<!-- setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output") -->

<!-- statn <- read_csv('statnall.csv') -->
<!-- grid <- read_csv('gridall.csv') -->

<!-- grid <- grid %>% mutate(site = 'grid') -->
<!-- statn <- statn %>% mutate(site = 'statn') -->

<!-- catchment <- bind_rows(grid, statn) %>% -->
<!--   mutate(year = as.factor(year(time))) %>% -->
<!--   group_by(year, site) %>% -->
<!--   mutate(cumulative_p = cumsum(precip)) -->

<!-- #plot cumulative precip by year -->
<!-- plot_cumprecip <- function(calyear) { -->
<!--   {catchment %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = time, -->
<!--                y = cumulative_p, color = site)) + -->
<!--     geom_line(size=1) + -->
<!--     ggtitle(calyear) + -->
<!--     ylab('Cumulative precip (mm)') + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1))} %>% -->
<!--     ggplotly() -->
<!-- } -->

<!-- name <- levels(catchment$year) -->

<!-- precip_plots <- lapply(name, plot_cumprecip) -->

<!-- htmltools::tagList(precip_plots) -->

<!-- precip_plots -->

<!-- ## total P -->
<!-- max_cumulativep <- catchment %>% -->
<!--   group_by(year, site) %>% -->
<!--   summarize(total_cumulativep = max(cumulative_p)) -->

<!-- ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) + -->
<!--   geom_point(size=3) + -->
<!--   ggtitle('Total cumulative precip (mm) by year') -->

<!-- ## Tmean -->

>>>>

@@

```{r hydrographs, echo = FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}

setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates')

@@

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            # "grid_2011"="seagreen",
                                            # "grid_2012"="seagreen2",
                                            # "grid_2013"="steelblue",
                                            # "grid_2014"='dodgerblue',
                                            # "grid_2015" = "cyan3",
                                            # 'grid_2016' = 'blue',
                                            # 'grid_2017' = 'blue4',
                                            # 'grid_2018' = 'cadetblue',
                                            # 'grid_2019' = 'lightgreen',
                                            # 'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            # "statn_2011"="maroon",
                                            # "statn_2012"="deeppink4",
                                            # "statn_2013"="deeppink",
                                            # "statn_2014"='purple',
                                            # "statn_2015" = "mediumorchid1",
                                            # 'statn_2016' = 'indianred',
                                            # 'statn_2017' = 'sienna',
                                            # 'statn_2018' = 'salmon2',
                                            # 'statn_2019' = 'mediumpurple1',
                                            # 'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
  theme_bw(base_size=20)

@@

#plot annual cumulative Q vals for ensembles
plot_cumulq_yr_ <- function(calyear) {
  {flow_cumq %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = cumsum,
               color = cal_run)) +
    geom_line() +
scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            # "grid_2011"="seagreen",
                                            # "grid_2012"="seagreen2",
                                            # "grid_2013"="steelblue",
                                            # "grid_2014"='dodgerblue',
                                            # "grid_2015" = "cyan3",
                                            # 'grid_2016' = 'blue',
                                            # 'grid_2017' = 'blue4',
                                            # 'grid_2018' = 'cadetblue',
                                            # 'grid_2019' = 'lightgreen',
                                            # 'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            # "statn_2011"="maroon",
                                            # "statn_2012"="deeppink4",
                                            # "statn_2013"="deeppink",
                                            # "statn_2014"='purple',
                                            # "statn_2015" = "mediumorchid1",
                                            # 'statn_2016' = 'indianred',
                                            # 'statn_2017' = 'sienna',
                                            # 'statn_2018' = 'salmon2',
                                            # 'statn_2019' = 'mediumpurple1',
                                            # 'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
    ggtitle(calyear) +
    theme_bw() +
    labs(y = 'Volume (m^3)')} %>%
    ggplotly()
}

@@

# flow_kge_all <- flow %>%
#   summarize(grid2011 = KGE(grid_2011, obs),
#             grid2012 = KGE(grid_2012, obs),
#             grid2013 = KGE(grid_2013, obs),
#             grid2014 = KGE(grid_2014, obs),
#             grid2015 = KGE(grid_2015, obs),
#             grid2016 = KGE(grid_2016, obs),
#             grid2017 = KGE(grid_2017, obs),
#             grid2018 = KGE(grid_2018, obs),
#             grid2019 = KGE(grid_2019, obs),
#             grid2020 = KGE(grid_2020, obs),
#             gridall = KGE(grid_all, obs),
#             statn2011 = KGE(statn_2011, obs),
#             statn2012 = KGE(statn_2012, obs),
#             statn2013 = KGE(statn_2013, obs),
#             statn2014 = KGE(statn_2014, obs),
#             statn2015 = KGE(statn_2015, obs),
#             statn2016 = KGE(statn_2016, obs),
#             statn2017 = KGE(statn_2017, obs),
#             statn2018 = KGE(statn_2018, obs),
#             statn2019 = KGE(statn_2019, obs),
#             statn2020 = KGE(statn_2020, obs),
#             statnall = KGE(statn_all, obs)) %>%
#     mutate_if(is.numeric,
#             round,
#             digits = 2)

flow_kge_all <- flow %>%
  summarize(
            gridall = KGE(grid_all,
                          obs, 
                          na.rm=T, 
                          method='2012'),
            statnall = KGE(statn_all, 
                           obs, 
                           na.rm=T,
                           method='2012')) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(
    # grid2011 = KGE(grid_2011, obs),
    #         grid2012 = KGE(grid_2012, obs),
    #         grid2013 = KGE(grid_2013, obs),
    #         grid2014 = KGE(grid_2014, obs),
    #         grid2015 = KGE(grid_2015, obs),
    #         grid2016 = KGE(grid_2016, obs),
    #         grid2017 = KGE(grid_2017, obs),
    #         grid2018 = KGE(grid_2018, obs),
    #         grid2019 = KGE(grid_2019, obs),
    #         grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs, na.rm = T, method='2012'),
            # statn2011 = KGE(statn_2011, obs),
            # statn2012 = KGE(statn_2012, obs),
            # statn2013 = KGE(statn_2013, obs),
            # statn2014 = KGE(statn_2014, obs),
            # statn2015 = KGE(statn_2015, obs),
            # statn2016 = KGE(statn_2016, obs),
            # statn2017 = KGE(statn_2017, obs),
            # statn2018 = KGE(statn_2018, obs),
            # statn2019 = KGE(statn_2019, obs),
            # statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs, na.rm=T, method='2012')) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

<!-- ### Annual KGE plots -->

<!-- ```{r wy plots, echo = FALSE, message = FALSE, warning = FALSE} -->

<!-- plot_kge <- function(calyear) { -->
<!--   flow_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = kge)) + -->
<!--     geom_point(size=3) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(flow_plot$year) -->

<!-- lapply(name, plot_kge) -->

@@

flow_pbias_all <- flow %>%
  summarize(
    # grid2011 = pbias(grid_2011, obs),
    #         grid2012 = pbias(grid_2012, obs),
    #         grid2013 = pbias(grid_2013, obs),
    #         grid2014 = pbias(grid_2014, obs),
    #         grid2015 = pbias(grid_2015, obs),
    #         grid2016 = pbias(grid_2016, obs),
    #         grid2017 = pbias(grid_2017, obs),
    #         grid2018 = pbias(grid_2018, obs),
    #         grid2019 = pbias(grid_2019, obs),
    #         grid2020 = pbias(grid_2020, obs),
            gridall = pbias(grid_all, obs),
            # statn2011 = pbias(statn_2011, obs),
            # statn2012 = pbias(statn_2012, obs),
            # statn2013 = pbias(statn_2013, obs),
            # statn2014 = pbias(statn_2014, obs),
            # statn2015 = pbias(statn_2015, obs),
            # statn2016 = pbias(statn_2016, obs),
            # statn2017 = pbias(statn_2017, obs),
            # statn2018 = pbias(statn_2018, obs),
            # statn2019 = pbias(statn_2019, obs),
            # statn2020 = pbias(statn_2020, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(
    # grid2011 = pbias(grid_2011, obs),
    #         grid2012 = pbias(grid_2012, obs),
    #         grid2013 = pbias(grid_2013, obs),
    #         grid2014 = pbias(grid_2014, obs),
    #         grid2015 = pbias(grid_2015, obs),
    #         grid2016 = pbias(grid_2016, obs),
    #         grid2017 = pbias(grid_2017, obs),
    #         grid2018 = pbias(grid_2018, obs),
    #         grid2019 = pbias(grid_2019, obs),
    #         grid2020 = pbias(grid_2020, obs),
            gridall = pbias(grid_all, obs),
            # statn2011 = pbias(statn_2011, obs),
            # statn2012 = pbias(statn_2012, obs),
            # statn2013 = pbias(statn_2013, obs),
            # statn2014 = pbias(statn_2014, obs),
            # statn2015 = pbias(statn_2015, obs),
            # statn2016 = pbias(statn_2016, obs),
            # statn2017 = pbias(statn_2017, obs),
            # statn2018 = pbias(statn_2018, obs),
            # statn2019 = pbias(statn_2019, obs),
            # statn2020 = pbias(statn_2020, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

<!-- ### Annual Pbias plots -->

<!-- ```{r pbias plots, echo = FALSE, message = FALSE, warning = FALSE} -->

<!-- plot_pbias <- function(calyear) { -->
<!--   flow_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = pbias)) + -->
<!--     geom_point(size=3) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(flow_plot$year) -->

<!-- lapply(name, plot_pbias) -->
